The \kepler Smear Campaign I: An Asteroseismic Catalogue of Bright Red Giants

### 2018-07-24 paper/ms.tex
stuff

Once \numax has been estimated, we use the asteroseismic scaling relation for \numax \citep[Equation~\ref{scaling};][]{KB95} to estimate \logg in order to inform extraction of chemical abundances from spectra. Using the initial spectroscopic estimate of \Teff, which is not significantly informed by \numax, we propagate uncertainties in \numax with Monte Carlo sampling.

>>>>

Once \numax has been estimated, we use the asteroseismic scaling relation for \numax \citep[Equation~\ref{scaling};][]{KB95} to estimate \logg in order to inform extraction of chemical abundances from spectra. Using the initial spectroscopic estimate of \teff, which is not significantly informed by \numax, we propagate uncertainties in \numax with Monte Carlo sampling.
